Automating Verification of MPC Security

### 2023-06-07 popl24/minicat.tex
checkpoint

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard
boolean algebra with $\eand$, $\eor$, $\exor$, and $\enot$ as
primitives. In addition programs have different kinds of variables,
including \emph{secrets} $\secret{\cid}{w}$, \emph{flips}
$\flip{\cid}{w}$, and \emph{views} $\view{\cid}{w}$.  Each of these
variables are indexed by an ``owner'' client $\cid$ and distinguishing
string $w$. So for example, $\secret{\ttt{1}}{\ttt{foo}}$ is client
$\ttt{1}$'s secret called $\ttt{foo}$. All clients can make reference
to the \emph{oracle} through variables $\oracle{w}$- this is a form
of shared randomness that is standard in the MPC setting \cite{XXX}.
Each client can only compute on their own variables in
\emph{expressions} $\be$, and share values with other clients by
assignment to their views as in $\eassign{\view{\cid}{w}}{\be}$.  A
\emph{protocol} $\prog$ is a possibly empty sequence of view
assignments.

>>>>

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition
programs have different kinds of variables, including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables are indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{foo}}$ is client $\ttt{1}$'s secret called
$\ttt{foo}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{XXX}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, i.e., writing $c_1;\ldots;\c_n$
instead of $c_1;\ldots;\c_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.
